Forcing for Isabelle

### 2018-12-29 LICS/intro_m.tex
typos

In pursuing the proof of Separation on generic extensions we
extended Paulson's library with:
\begin{inlinelist}
\item renaming of variables for \emph{internalized} formulas, which
  with little effort can be extended 
  to substitutions;
\item an improvement on definitions by recursion on well-founded
  relations; 
\item enhancements in the hierarchy of locales; and
\item a variant of the  principle of dependent choices and a version
  of Rassiowa-Sikorski, which 
  ensures the existence of generic filters for countable and transitive
  models of $\ZF$;
\end{inlinelist} 
the last item was already communicated in the
  first report \cite{2018arXiv180705174G}.

>>>>

In pursuing the proof of Separation on generic extensions we
extended Paulson's library with:
\begin{inlinelist}
\item renaming of variables for \emph{internalized} formulas, which
  with little effort can be extended 
  to substitutions;
\item an improvement on definitions by recursion on well-founded
  relations; 
\item enhancements in the hierarchy of locales; and
\item a variant of the  principle of dependent choices and a version
  of Rasiowa-Sikorski, which 
  ensures the existence of generic filters for countable and transitive
  models of $\ZF$;
\end{inlinelist} 
the last item was already communicated in the
  first report \cite{2018arXiv180705174G}.
